Parameterization of the responses of subarctic European vegetation to key environmental variables for ozone risk assessment

### 2022-04-24 VegOzone.tex
Typo

Temperature anomalies (Fig.~\ref{fig:anomalies_svanvik}a) show enhanced temperatures through out summer (May--September) 2018 breaching the IQR two times while March was unusually cold. No notably enhanced temperatures occurred in 2019 indicating that 2019 was an average year.

>>>>

Temperature anomalies (Fig.~\ref{fig:anomalies_svanvik}a) show enhanced temperatures throughout summer (May--September) 2018 breaching the IQR two times while March was unusually cold. No notably enhanced temperatures occurred in 2019 indicating that 2019 was an average year.
